\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
% This is a custom font. Try use `updmap` in command line if build fails after installing font package
\usepackage{fontawesome7}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% This is a custom font. Try use `updmap` in command line if build fails after installing font package
\usepackage[sfdefault]{roboto}  %% Option 'sfdefault' only if the base font of the document is to be sans serif
\usepackage[T1]{fontenc}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.525in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-5pt}\large\bfseries
}{}{0em}{}[{\color{black} \titlerule[0.5pt] \vspace{-5pt}}]

%-------------------------
% Custom commands
\newcommand{\myItem}[1]{
  \item\raggedright\small{#1\vspace{-5pt}}
}

\newcommand{\mySecondaryItem}[1]{
  \item\raggedright\small{#1\vspace{-.5pt}}
}

\newcommand{\experienceSubHeading}[5]{
  \item[]
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} | {#2} & {#3} \\
    \small{\textit{#4}} & \textit{\small{#5}} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\educationSubHeading}[3]{
  \item[]
  \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1}, {\small #2} & \textit{\small #3}
  \end{tabular*}\vspace{-5pt}
}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\experienceListStart}{\begin{itemize}[leftmargin=0]}
\newcommand{\experienceListEnd}{\end{itemize}}
\newcommand{\educationListStart}{\begin{itemize}[leftmargin=0]}
\newcommand{\educationListEnd}{\end{itemize}}
\newcommand{\itemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\itemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


%----------HEADING-----------------
\textbf{\Large \centerline{Tianxiu (Tyson) Zhou}}\\
\vspace{8pt}\centerline{
  \faPhone\hspace{4pt} (510)502-6832
  \hspace{8pt}
  \faEnvelope\hspace{4pt} \href{mailto:choutianxius@gmail.com}{choutianxius@gmail.com}
  \hspace{8pt}
  \faLinkedinIn\hspace{4pt} \href{https://www.linkedin.com/in/tianxiu-zhou}{tianxiu-zhou}
  \hspace{8pt}
  \faGithub\hspace{4pt} \href{https://github.com/choutianxius}{choutianxius}
}

%-----------Experiences-----------------
\section{Experiences}
\experienceListStart

\experienceSubHeading
{Software Engineer}
{Instagram Parent and Guardian Experience}
{\small{\faMeta} Meta Platforms, Inc.}
{In-product marketing, PHP, Python, iOS, Android, React.js}
{Jul 2025 - Current}
\itemListStart
\mySecondaryItem{
  Uplift parent and teen's sentiment and alignment on Instagram through in-app marketing promotions. Optimize marketing strategies with A/B testing experiments, holdout experiments and surveys.
}
\mySecondaryItem{
  Build and maintain supervision features for teens and parents/guardians on Instagram across mobile and web platforms.
}
\mySecondaryItem{
  Contribute to better engineering efforts to improve reliability and scalability. Integrate LLMs with code quality issue detection pipelines and improve the team's adoption of AI-driven development.
}
\itemListEnd

\experienceSubHeading
{Software Development Intern}
{Advanced Mobile Automated Regression Testing}
{Paycom LLC.}
{.NET, Docker, GitLab, MySQL, TypeScript, React.js}
{May 2024 -- Aug 2024}
\itemListStart
\mySecondaryItem{
  Collaboratively designed a system for executing UI regression tests on remote mobile devices, providing a unified solution to automating quality assurance tests with comprehensive control and logging for both iOS and Android.
}
\mySecondaryItem{
  Developed a .NET Core backend application with the MySQL database to provide a RESTful API for managing test scripts, scheduling and dispatching testing jobs to mobile devices, and persisting test execution results.
}
\mySecondaryItem{
  Implemented dependency injection and the repository pattern in the .NET Core backend project. Implemented unit tests with xUnit and Moq to achieve a full test coverage.
}
\mySecondaryItem{
  Set up GitLab CI pipelines to automatically perform unit testing and linting upon merge requests.
}
\mySecondaryItem{
  Built an SPA frontend for visualizing test scripts, testing jobs and results with React.js and an internal UI library.
}
\mySecondaryItem{
  Containerized the .NET Core backend using Docker and integrated the frontend SPA with Docker multi-stage building.
}
\mySecondaryItem{
  Awarded as one of the MVPs of the Software Development Internship program.
}
\itemListEnd

\experienceSubHeading
{Research Assistant}
{Digital Twin-Based Smart City \& Smart Construction Platform
}
{Texas A\&M Univ.}
{TypeScript, Next.js, React Native, TailwindCSS, FastAPI, Apache Kafka, Redis, AWS}
{Nov 2023 -- May 2025}
\itemListStart
\mySecondaryItem{
  Designed and implemented a FastAPI backend to deliver domain-specific data analysis via RESTful APIs.
}
\mySecondaryItem{
  Engineered an asynchronous data processing pipeline using Apache Kafka and Redis, with outputs persisted to AWS DynamoDB.
}
\mySecondaryItem{
  Built responsive web interfaces including a public data visualization site and an internal admin dashboard using Next.js and TailwindCSS.
}
\mySecondaryItem{
  Developed a cross-platform mobile app with React Native for interactive data visualization; created a high-performance custom charting library using React Native Skia and D3.js.
}
\mySecondaryItem{
  Deployed full-stack applications using AWS services including ECS, S3, CloudFront, Route 53, and Amplify.
}
\mySecondaryItem{
  Established CI/CD pipelines with AWS CodeCommit, CodeBuild, and CodeDeploy to automate testing, integration, and deployment workflows.
}
\itemListEnd

\experienceListEnd

%-----------Projects-----------------
\section{Projects}
\experienceListStart

\experienceSubHeading
{B.S. Thesis Research}
{Network Dissection of a DQN Agent for Super Mario Bros
  \small \href{https://github.com/choutianxius/thuthesis-mario}{\faGithub}
}
{Tsinghua Univ.}
{PyTorch, Deep Reinforcement Learning, OpenAI Gym, Numpy}
{Feb 2023 -- Jun 2023}
\itemListStart
\mySecondaryItem{
  Implemented the double DQN algorithm with PyTorch to train a reinforcement learning agent to beat Super Mario Bros.}
\mySecondaryItem{
  Fine-tuned a semantic segmentation model for segmenting in-game scenes to generate training dataset for the DQN agent, based on ResNet-50.
}
\mySecondaryItem{
  Examined the correlation between activation of neurons in the DQN network and objects in the input scenes, in an effort to investigate the mechanism of neuron function generation.
}
\itemListEnd

\experienceListEnd

%-----------EDUCATION-----------------
\section{Education}
\educationListStart
\educationSubHeading{Texas A\&M University}{Master of Computer Science}{Aug 2023 -- May 2025}
\educationSubHeading{Tsinghua University}{Bachelor of Science in Biology}{Aug 2019 -- Jun 2023}
\educationListEnd


%-------------------------------------------
\end{document}
